\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-09 paper.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{¿Está bien la polaridad de la batería?}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = \frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

\notaL{ref}. The potential within the electrolytic cell coincides the

@@

$2a\times2b\times4c$ with a basis of 16 point charges arranged in
positive and negative planes.

\textbf {Problem considerations}: The problem is the potential, the
field and the current produced by a periodic 2D network of a real load
and all its images. The potential due to a periodic network is
automatically found in the plane making a sum of 2D Fourier.
 \rho(\vec{r}) =q \displaystyle\sum_{R}  \ \delta
  (\vec{r}-\vec{R}-\vec{r}_0) =\dfrac{q}{A}  \displaystyle\sum_{G}
  e^{i G \cdot (\vec{r}-\vec{r}_{0})} \delta (z-z_0)
Where $ {R} $ is the 2D Bravais network and $ {G} $ its reciprocal
network. It is written $ \phi (\vec{r}) = \displaystyle \sum _
{\vec{G}}  \phi_{_{G}}(z) e^{i \vec {G} \cdot \vec {r}} $. So the
Poisson equation $ \nabla^2 \phi = -4 \pi \displaystyle
\sum_{\vec{R}} \delta (\vec{r} - \vec{R} - \vec{r}_0) $.
Becomes
 \dfrac{\partial^2 \phi_{_{G}}(z)}{\partial z^2}+ G^2\phi_{_{G}}(z)=
   -\dfrac{4 \pi}{A}  q   e^{i \vec{G} \cdot \vec{r}_{_0}} \delta
   (z-z_0)
Solving the homogeneous equation above and below $ z = z_0 $, using
symmetry and conditions at $ \pm \infty $ we obtain $ \phi_{_{G}} =
\phi_{_{G}}^{0} e^{ G \abs{z-z_0}} \ \ \ \ \ (G \neq 0) $. And
adjusting the singularity
 \phi_{_{G}}(z)= \dfrac{2 \pi q}{AG}  e^{- G \abs{z-z_0}} e^{-i
   \vec{G} \cdot \vec{r}_{_0}} \ \ \ \ \ (G\neq 0)
For the case $ G = 0 $ is similar $ \phi_{_{G = 0}} (z) = \dfrac{-2
  \pi q}{A} \abs{z-z_0} + K, $ $ \ \ $ (K is a constant). Here $ A =
L_x L_y $ is the unit cell area
 \phi(\vec{r}) = K-\dfrac{2 \pi q}{A}  \abs{z-z_0} +\dfrac{2 \pi
   q}{A}\displaystyle\sum_{\vec{G}} \dfrac{1}{G} e^{- G \abs{z-z_0}}
   e^{i \vec{G} \cdot \vec{r}-\vec{r}_0}
Adding all the images loads,

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\usepackage{bm}
\usepackage{ulem} %opcional para la correcciones
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}+L:#1+}}
\title{\textbf{Optimization of Porous Silicon Gradient Refractive
    Index Structures.} }
% A comparison with computational schemes with experimental results
\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

@@

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a good conductor which is
electrically grounded. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/celdan1}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $ \vec{r}_0 $ within the
    liquid.\notaL{\sout{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}}\notaL{\sout{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}}\notaL{\sout{Indica el voltaje y la
    corriente}}\notaL{\sout{¿Está bien la polaridad de la batería?}}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = \frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = \frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

\notaL{\sout{ref}}. The potential within the electrolytic cell coincides the

@@

$2a\times2b\times4c$ with a basis of 16 point charges of charge $\pm
q_0$ arranged in positive and negative planes.

The electrostatic potential produced by an infinite array of
charges expressed as a sum in real space of Coulomb terms has ill
convergence properties. The potential can be obtained
using the Ewald summation technique \cite{T3,T4,T5}\notaL{\sout{ref}}, which yields
 two rapidly convergingseries, one in real space and another one in reciprocal space.
Nevertheless, as we need the potential and the field to obtain the
current density on the surface of the sample on which there are no
real nor image charges, we may perform a somewhat simpler planewise
summation, where we first obtain the potential and field produced by a
simple periodic lattice of charges using a fast convergent sum over the 2D
reciprocal vectors, and then sum over the charges that form the basis
of the 2D {\em crystal} plane and finally sum over all the
 planes \cite{T6,T7} \notaL{\sout{ref}}.

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{_{\bm G}}(z)e^{i\bm G\cdot\bm r_\|} 
\end{equation}
where $\phi_{_{\bm G}}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{_{\bm G}}(z)-G^2\phi_{_{\bm G}}(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the symmetric solution that decays far from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

We consider now the basis of our 2D lattice, with equal charges at the
four positions $(\pm x_0, \pm y_0)$. Each of the corresponding four
sublattices produces a potential as that in Eq. \eqref{eq:phiG1} but
shifted by the corresponding basis vector, yielding
\begin{equation}
  \label{eq:phiG4}
  \phi(\bm r) = -\frac{8\pi}{A} \abs{z}
    +{\sum_{\bm G}}' \frac{8\pi}{AG} e^{- G \abs{z}}\cos(G_x x_0)
    \cos(G_y y_0) e^{i \bm G\cdot\bm r_\|}.
\end{equation}
Finally, we shift the origin of Eq. \eqref{eq:phiG4} vertically to each of the planes shown in
Fig. \ref{fig:sideview} and multiply by the corresponding charge $q_0$
or $-q_0$ to obtain the contribution to the total potential. The charge $q_0$ corresponds to
the planes with heights of the form $z_0+4nc$ and $-z_0+(4n+2)c$, with
$n=\ldots-2,-1,0,1,2\ldots$ an arbitrary integer, while the charge
$-q_0$ corresponds to the planes with height $z_0+(4n+2)c$ and
$-z_0+(4n+4)c$.

We concentrate our attention only on the region $a\le z<z_0$. From
Fig. \ref{fig:sideview} we see that the $G=0$
field has contributions only from the charges at $z_0$ and their
images ant $-z_0$, this contribution is like that of a parallel plate
capacitor $E_{0z}=-4\pi q_0/ab=-16\pi q_0/A$, which corresponds to the
potential $\phi_0=16\pi q_0 z/A$. Other contiguous planes of with opposite charges
contribute to the field elsewhere. The contributions to the potential
from the $G\ne0$ are simple geometric sums that may be summed
analytically over $n$ and yield the total potential
\begin{equation}
  \label{eq:phitot}
  \begin{split}
    \phi(\bm r)=&\frac{16\pi q_0}{A}\biggl(z+{\sum_{\bm G}}'\frac{2\sinh
      Gc}{G \sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
    &\times \sinh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
  \end{split}
\end{equation}

\notaL{Aquí voy. Checa la ecuación previa}

In our case of
interest we take $0\le z < z_0$ and thus write

@@

 \bibitem{T3} Mahfoud Belhadj, Howard E. Alper, and Ronald M. Levy. \textquotedblleft 
 \emph{ Molecular dynamics simulations of water with Ewald summation 
 	for the long range electrostatic interactions.}\textquotedblright Chemical
  Physics Letters, 179(1-2):13–20, 1991.
   \bibitem{T4}A. Bródka.\textquotedblleft 
   \emph{ Ewald summation method with electrostatic layer correction for
  interactions of point dipoles in slab geometry.}\textquotedblright Chemical 
Physics Letters, 400(1):62–67, December 2004.
 \bibitem{T5} A. Grzybowski, E. Gwóźdź, and A. Bródka.\textquotedblleft 
 \emph{ Ewald summation of electrostatic interactions in molecular dynamics
 	 of a three-dimensional system with periodicity in two directions.}\textquotedblright 
  Physical Review B, 61(10):6706–6712, March 2000.

 \bibitem{T6} Kratzer, Peter, and Jörg Neugebauer. \textquotedblleft \emph{The basics of 
 	electronic structure theory for periodic systems.}\textquotedblright 
  Frontiers in chemistry 7 (2019).
 \bibitem{T7} Charles Kittel. \textquotedblleft \emph{Introduction to Solid State
 	 Physics.}\textquotedblright Wiley, Hoboken, NJ, 8 edition, 2005.
